### 2017-01-27 kalman_walk.tex
.

% is y the phenotype or H(z) the phenotype? Do we need new jargon anyway? 
% 
% Deleterious mutations: can we describe heterosis?

@@

\begin{lemma}
    Let $(A,B,C)$ be a system.
    Every matrix $\widehat A$ such that $(\widehat A,B,C)$ is equivalent to $(A,B,C)$
    can be specified in the form given in Theorem \ref{thm:kalman},
    with \plr{them having the same $\ro$ bit}
    and satisfying
    \begin{align*}
        P^{-1} \widehat B &= B \\
        \widehat C P &= C
    \end{align*}
\end{lemma}

@@

@@

>>>>

% is y the phenotype or H(z) the phenotype? Do we need new jargon anyway? 
%

@@

\begin{lemma}
    Let $(A,B,C)$ be a system.
    Every matrix $\widehat A$ such that $(\widehat A,B,C)$ is equivalent to $(A,B,C)$
    can be specified in the form given in Theorem \ref{thm:kalman},
    with \plr{them having the same $\ro$ bit}
    and satisfying
    \begin{align*}
        \widehat B &= P B \\
        \widehat C P &= C
    \end{align*}
\end{lemma}

@@

\plr{General argument why Brownian motion on set of equivalent things is maybe ok.}

\begin{example}
    The system in Example \ref{ex:2x2} is minimal, so $A=A_\ro$,
    and the only free parameter is $P$.
    Suppose also that the effects of the input and output are strongly constrained,
    so that as in that example,
    $B$ and $C$ cannot change,
    and neutral evolution moves through the set of of $P$ such that $PB=B$ and $CP=C$.
    \plr{Clarify we mean with no gene duplication and only neutral drift.}
    How will this system change over evolutionary time in the manner described \plr{above}?
    An unbiased Brownian motion on this set 
    can be written in terms of a one-dimensional Brownian motion $\beta_\tau$ 
    with $\beta_0=0$ as
    \begin{align*}
        P(\tau) = \left[
            \begin{array}{cc}
                1 & 0 \\
                e^{\beta_\tau}-1 & e^{\beta_\tau}
            \end{array}
            \right] .
    \end{align*}
    Therefore, the state of the system after (evolutionary) time $\tau$
    is $(P(\tau)AP(\tau)^{-1},B,C)$.
\end{example}

@@

\section{Notes on what to do when allowing deleterious mutations}

Epistasis, coming from mutations deleterious in some networks but not in others
(come from incompatibilities).

Describe heterosis.
